### 2020-03-30 model.tex
Add static model and steady-state results

Focusing our attention on Moltres, the neutron flux calculations are
performed using the standard formulations for the time-dependent multigroup
neutron diffusion equations and \gls{DNP} concentration equations as shown in
equations \ref{eq:neut} and \ref{eq:dnp}:
%
\begin{align}
    \frac{1}{v_g} \frac{\partial \phi_g}{\partial t} &= \nabla \cdot D_g
    \nabla \phi_g - \Sigma^r_g \phi_g +
    \sum^G_{g' \neq g} \Sigma^s_{g' \rightarrow g} \phi_{g'} + \chi^p_g
    \sum^G_{g'=1} (1-\beta) \nu \Sigma^f_{g'} \phi_{g'} + \chi^d_g \sum^I_i
    \lambda_i C_i, \label{eq:neut} \\
    \frac{\partial C_i}{\partial t} &= \beta_i \sum^G_{g'=1} \nu \Sigma^f_{g'}
    \phi_{g'} - \lambda_i C_i - \boldsymbol{u} \cdot \nabla C_i + \nabla \cdot
    D_t \nabla C_i, \label{eq:dnp} \\
    \intertext{where}
    v_g &= \text{average speed of neutrons in group $g$ [cm s$^{-1}$],} 
    \nonumber \\
    \phi_g &= \text{neutron flux in group $g$ [cm$^{-2}$ s$^{-1}$],} \nonumber
    \\
    t &= \text{time [s],} \nonumber \\
    D_g &= \text{diffusion coefficient of neutrons in group $g$ [cm$^2$
    s$^{-1}$],} \nonumber \\
    \Sigma^r_g &= \text{macroscopic cross section for removal of neutrons from
    group $g$ [cm$^{-1}$],} \nonumber \\
    \Sigma^s_{g' \rightarrow g} &= \text{macroscopic cross section of
    scattering from $g'$ to $g$ [cm$^{-1}$],} \nonumber \\
    \chi^p_g &= \text{prompt fission spectrum for neutrons in group $g$,}
    \nonumber \\
    G &= \text{total number of discrete neutron groups,} \nonumber \\
    \nu &= \text{average number of neutrons produced per fission,} \nonumber
    \\
    \Sigma^f_{g} &= \text{macroscopic fission cross section for neutron in
    group $g$ [cm$^{-1}$],} \nonumber \\
    \chi^d_g &= \text{delayed fission spectrum for neutrons in group $g$,}
    \nonumber \\
    I &= \text{total number of delayed neutron precursor groups,} \nonumber \\
    \beta &= \text{total delayed neutron fraction,} \nonumber \\
    \beta_i &= \text{delayed neutron fraction of precursor group $i$,}
    \nonumber \\
    \lambda_i &= \text{average decay constant of delayed neutron precursors in
    precursor group $i$,} \nonumber \\
    C_i &= \text{concentration of delayed neutron precursors in precursor
    group $i$,} \nonumber \\
    D_t &= \text{turbulent diffusion of the delayed neutron precursors [cm$^2$
    s$^{-1}$].} \nonumber
\end{align}
%

@@

The \gls{DNP} concentration equation has additional advection and turbulent
diffusion terms to account for the movement of \glspl{DNP} in the primary
coolant loop. The turbulent diffusion value is governed by the following
equation:
%
\begin{align}
    D_t &= \frac{\mu_t}{\rho Sc_t}
\end{align}
%
where $\mu_t$ is the eddy viscosity [kg cm$^{-1}$ s$^{-1}$] , $\rho$ is the
density of the fuel salt [kg cm$^{-3}$], and $Sc_t$ is the turbulent Schmidt
number. We assumed $Sc_t = 0.85$ for a fair comparison with the Polimi/TUDelft
models which used the same value. Moltres also accounts for the decay of
\glspl{DNP} outside the active core region by simulating its flow in a
separate 1-D pipe geometry. This outer loop pipe simulation is loosely coupled
to the active core simulation through MOOSE's MultiApp functionality and
inlet/outlet boundary values. The loose coupling is justified as the evolution
of \gls{DNP} concentrations due to inflow is relatively slow. The length and
velocity defined in this geometry may differ according to reactor
specifications. For this work with the \gls{MSFR} model, we assumed a pipe
length of 2.255 m with salt flowing at 1.1275 m s$^{-1}$ for an out-of-core
residence time of 2 seconds to follow the design specifications.

@@

Like the neutron and \gls{DNP} groups, Moltres can take an arbitrary number of
decay heat groups. In this work, as with the other parameters, we used the
same decay heat fractions and decay constants used in the Polimi/TUDelft
models for three decay heat groups.

@@

Fluid dynamics in Moltres can be modeled using the \gls{INS} equations with
the Boussinesq hypothesis for eddy viscosity. Most of the Navier-Stokes
capabilities in Moltres is derived from the MOOSE Navier-Stokes module
\cite{peterson_overview_2017}. The standard \gls{INS} equations are:
%
\begin{align}
    \text{Momentum eq.:} && \rho \frac{\partial \boldsymbol{u}}{\partial t} &=
    -\rho (\boldsymbol{u}
    \cdot \nabla) \boldsymbol{u} + \nabla \cdot (-p \boldsymbol{I} + \mu [
    \nabla \boldsymbol{u} + (\nabla \boldsymbol{u})^T] + \boldsymbol{f} &&
    \label{eq:momemtum} \\
    \text{Divergence-free:} && \nabla \cdot \boldsymbol{u} &= 0 &&
    \label{eq:divergence}
    \intertext{where}
    && p &= \text{ pressure} && \nonumber \\
    && \mu &= \text{ dynamic viscosity} && \nonumber \\
    && \boldsymbol{f} &= \text{ body force per unit volume} && \nonumber
\end{align}

@@

The flow rate is dictated by an inflow boundary condition at the core inlet
for a volumetric flow rate of 4.5 m$^3$ s$^{-1}$. We imposed no-slip boundary
conditions on the walls of the core, and homogeneous Neumann boundary
conditions on the core outlet. The energy balance equation for temperature is
given in Eq. \ref{eq:temp}. The diffusion term includes turbulent heat
diffusivity based on the eddy viscosity $\mu_t$ and the turbulent Prandtl
number $Pr_t$, which we assume to be equal to 0.85. 
%
\begin{align}
    \rho c_{p} \frac{\partial T}{\partial t} &= - \rho c_p \boldsymbol{u}
    \cdot \nabla T + \nabla \cdot [(k + k_t) \nabla T] + Q_s - Q_{hx}
    \label{eq:temp} \\
    k_t &= \frac{\mu_t}{\rho Pr_t} \\
    Q_s &= \Big( 1 - \sum^K_{k=1} f_k \Big) \sum^G_{g=1} \epsilon_g \Sigma_g^f
    \phi_g + \sum^K_{k=1} \omega_k, \label{eq:source}
    \intertext{where}
    \rho &= \text{density of molten salt} \nonumber \\
    c_{p} &= \text{specific heat capacity of molten salt} \nonumber \\
    T &= \text{temperature of molten salt} \nonumber \\
    \boldsymbol{u} &= \text{velocity of molten salt} \nonumber \\
    k &= \text{thermal conductivity of molten salt} \nonumber \\
    Q_{hx} &= \text{heat sink} \nonumber \\
\end{align}
%
where $K$ is the total number of decay heat groups. The first term in the heat
source expression represents prompt fission heat, and the second term
represents decay heat from the $K$ decay heat groups.

>>>>

Focusing our attention on Moltres, the neutron flux calculations are
performed using the standard formulations for the time-dependent multigroup
neutron diffusion equations and \gls{DNP} concentration equations as shown in
equations \ref{eq:neut} and \ref{eq:dnp}:
%
\begin{align}
    \frac{1}{v_g} \frac{\partial \phi_g}{\partial t} &= \nabla \cdot D_g
    \nabla \phi_g - \Sigma^r_g \phi_g +
    \sum^G_{g' \neq g} \Sigma^s_{g' \rightarrow g} \phi_{g'} + \chi^p_g
    \sum^G_{g'=1} (1-\beta) \nu \Sigma^f_{g'} \phi_{g'} + \chi^d_g \sum^I_i
    \lambda_i C_i, \label{eq:neut} \\
    \frac{\partial C_i}{\partial t} &= \beta_i \sum^G_{g'=1} \nu \Sigma^f_{g'}
    \phi_{g'} - \lambda_i C_i - \boldsymbol{u} \cdot \nabla C_i + \nabla \cdot
    D_t \nabla C_i, \label{eq:dnp} \\
    \intertext{where}
    v_g &= \text{average speed of neutrons in group $g$ [cm s$^{-1}$],} 
    \nonumber \\
    \phi_g &= \text{neutron flux in group $g$ [cm$^{-2}$ s$^{-1}$],} \nonumber
    \\
    t &= \text{time [s],} \nonumber \\
    D_g &= \text{diffusion coefficient of neutrons in group $g$ [cm$^2$
    s$^{-1}$],} \nonumber \\
    \Sigma^r_g &= \text{macroscopic cross section for removal of neutrons from
    group $g$ [cm$^{-1}$],} \nonumber \\
    \Sigma^s_{g' \rightarrow g} &= \text{macroscopic cross section of
    scattering from $g'$ to $g$ [cm$^{-1}$],} \nonumber \\
    \chi^p_g &= \text{prompt fission spectrum for neutrons in group $g$,}
    \nonumber \\
    G &= \text{total number of discrete neutron groups,} \nonumber \\
    \nu &= \text{average number of neutrons produced per fission,} \nonumber
    \\
    \Sigma^f_{g} &= \text{macroscopic fission cross section for neutron in
    group $g$ [cm$^{-1}$],} \nonumber \\
    \chi^d_g &= \text{delayed fission spectrum for neutrons in group $g$,}
    \nonumber \\
    I &= \text{total number of delayed neutron precursor groups,} \nonumber \\
    \beta &= \text{total delayed neutron fraction,} \nonumber \\
    \beta_i &= \text{delayed neutron fraction of precursor group $i$,}
    \nonumber \\
    \lambda_i &= \text{average decay constant of delayed neutron precursors in
    precursor group $i$ [s$^{-1}$],} \nonumber \\
    C_i &= \text{concentration of delayed neutron precursors in precursor
    group $i$ [cm$^{-3}$],} \nonumber \\
    D_t &= \text{turbulent diffusion of the delayed neutron precursors [cm$^2$
    s$^{-1}$].} \nonumber
\end{align}
%

@@

The \gls{DNP} concentration equation has additional advection and turbulent
diffusion terms to account for the movement of \glspl{DNP} in the primary
coolant loop. The turbulent diffusion value is governed by the following
equation:
%
\begin{align}
    D_t &= \frac{\mu_t}{\rho Sc_t}
    \intertext{where}
    \mu_t &= \text{ eddy viscosity [Pa s],} \nonumber \\ 
    \rho &= \text{ density of the fuel salt [kg m$^{-3}$],} \nonumber \\
    Sc_t &= \text{ turbulent Schmidt number.} \nonumber
\end{align}
%

We assumed $Sc_t = 0.85$ for a fair comparison with the Polimi/TUDelft
models which used the same value. Moltres also accounts for the decay of
\glspl{DNP} outside the active core region by simulating its flow in a
separate 1-D pipe geometry. This outer loop pipe simulation is loosely coupled
to the active core simulation through MOOSE's MultiApp functionality and
inlet/outlet boundary values. The loose coupling is justified as the evolution
of \gls{DNP} concentrations due to inflow is relatively slow. The length and
velocity defined in this geometry may differ according to reactor
specifications. For this work with the \gls{MSFR} model, we assumed a pipe
length of 2.255 m with salt flowing at 1.1275 m s$^{-1}$ for an out-of-core
residence time of 2 seconds to follow the design specifications.

@@

Like the neutron and \gls{DNP} groups, Moltres can take an arbitrary number of
decay heat groups. In this work, as with the other parameters, we used the
same decay heat fractions and decay constants, shown in Table
\ref{eq:decayheat}, used in the Polimi/TUDelft models for three decay heat
groups.

@@

Fluid dynamics in Moltres can be modeled using the \gls{INS} equations with
the Boussinesq hypothesis for eddy viscosity. Most of the Navier-Stokes
capabilities in Moltres is derived from the MOOSE Navier-Stokes module
\cite{peterson_overview_2017}. The standard \gls{INS} equations are:
%
\begin{align}
    \text{Momentum eq.:} && \rho \frac{\partial \boldsymbol{u}}{\partial t} &=
    -\rho (\boldsymbol{u}
    \cdot \nabla) \boldsymbol{u} + \nabla \cdot (-p \boldsymbol{I} + \mu [
    \nabla \boldsymbol{u} + (\nabla \boldsymbol{u})^T] + \boldsymbol{f} &&
    \label{eq:momemtum} \\
    \text{Divergence-free:} && \nabla \cdot \boldsymbol{u} &= 0 &&
    \label{eq:divergence}
    \intertext{where}
    && p &= \text{ pressure [Pa],} && \nonumber \\
    && \mu &= \text{ dynamic viscosity [Pa s],} && \nonumber \\
    && \boldsymbol{f} &= \text{ body force per unit volume [N m$^{-3}$].} &&
    \nonumber
\end{align}

@@

The flow rate is dictated by an inflow boundary condition at the core inlet
for a volumetric flow rate of 4.5 m$^3$ s$^{-1}$. We imposed no-slip boundary
conditions on the walls of the core, and homogeneous Neumann boundary
conditions on the core outlet. The energy balance equation for temperature is
given in Eq. \ref{eq:temp}. The diffusion term includes turbulent heat
diffusivity based on the eddy viscosity $\mu_t$ and the turbulent Prandtl
number $Pr_t$, which we assume to be equal to 0.85. 
%
\begin{align}
    \rho c_{p} \frac{\partial T}{\partial t} &= - \rho c_p \boldsymbol{u}
    \cdot \nabla T + \nabla \cdot [(k + k_t) \nabla T] + Q_s - Q_{hx}
    \label{eq:temp} \\
    k_t &= \frac{\mu_t}{\rho Pr_t} \\
    Q_s &= \Big( 1 - \sum^K_{k=1} f_k \Big) \sum^G_{g=1} \epsilon_g \Sigma_g^f
    \phi_g + \sum^K_{k=1} \omega_k, \label{eq:source}
    \intertext{where}
    c_p &= \text{specific heat capacity of molten salt [J kg$^{-1}$ K$^{-1}$],
    } \nonumber \\
    T &= \text{temperature of molten salt [K]} \nonumber \\
    \boldsymbol{u} &= \text{velocity of molten salt [m s$^{-1}$],} \nonumber
    \\
    k &= \text{thermal conductivity of molten salt [W m$^{-1}$ K$^{-1}$,}
    \nonumber \\
    Q_{hx} &= \text{heat loss rate through the heat exchanger [W].} \nonumber
\end{align}
%
where $K$ is the total number of decay heat groups. The first term in the heat
source expression represents prompt fission heat, and the second term
represents decay heat from the $K$ decay heat groups.

### 2020-03-30 results.tex
Add static model and steady-state results

We calculated estimates of $k_{\text{eff}}$ values in Serpent and Moltres for
the \gls{MSFR} model with static salt (no flow), a uniform temperature
distribution of 973 K, and a fuel salt density of $4.1249 \times 10^3$ kg
m$^{-3}$. Moltres performs eigenvalue calculations for finding the 
$k_{\text{eff}}$ as it does not currently have the capability to calculate
the adjoint flux. Table \ref{table:keff} shows the $k_{\text{eff}}$ values
from Serpent, and from Moltres with and without \glspl{DNP}. We observe a
small 127.9 pcm discrepancy between the two codes, which we attribute to two
main factors: the neutron diffusion model, and the omission of the blanket
tank structural material. It is well-known that the neutron diffusion model is
not as accurate as the other S$_{\text{N}}$ or SP$_{\text{N}}$ deterministic
methods nor the Monte Carlo approach in Serpent. Regarding the omission of the
blanket tank material, we replaced the 2 cm-thick structural material with
blanket salt. This decision may be partly responsible for the higher
$k_{\text{eff}}$ value calculated by Moltres. Nevertheless, the discrepancy is
smaller than the 228.5 pcm and 256.7 pcm discrepancy reported by Cervi et al.
\cite{cervi_development_2019} for their six-group $SP_3$ and neutron diffusion
methods, respectively, in OpenFOAM. The neutron diffusion model in OpenFOAM is
the same approach Aufiero et al. \cite{aufiero_development_2014} used for
their transient analysis of the \gls{MSFR}, albeit with one neutron energy
group.

\begin{table}[htb!]
	\centering
	\caption{$k_{\text{eff}}$ values from Serpent and Moltres.}
	\begin{tabular}{l S S}
		\toprule
		{Code} & {$k_{\text{eff}}$} & {Diff. wrt Serpent [pcm]}\\
		\midrule
		{Serpent} & 1.00667 \pm 0.000049 & 0\\
		{Moltres with \glspl{DNP}} & 1.007949 \pm 0.000001 & 127.9\\
		{Moltres without \glspl{DNP}} & 1.004937 \pm 0.000001 & {-}\\
		\bottomrule
	\end{tabular}
	\label{table:keff}
\end{table}
%
\begin{table}[htb!]
	\centering
	\caption{$\beta_{\text{eff}}$ values from Serpent and Moltres.}
	\begin{tabular}{l S S}
		\toprule
		{Code} & {$\beta_{\text{eff}}$ [pcm]} & {Diff. wrt Serpent [pcm]}\\
		\midrule
		{Serpent} & 303.2 \pm .8 & 0\\
		{Moltres} & 301.2 \pm .2 & 2.0\\
		\bottomrule
	\end{tabular}
	\label{table:betaeff}
\end{table}

The

\section{Steady-State Behavior}

@@

\section{Transient Behavior}

>>>>

We calculated estimates of $k_{\text{eff}}$ values in Serpent and Moltres for
the \gls{MSFR} model with static salt (no flow), and uniform temperature
distributions. Moltres solves the six-group neutron diffusion equations as a
steady-state eigenvalue problem to find the $k_{\text{eff}}$ as it does not
currently have the capability to calculate the adjoint flux. Table
\ref{table:keff} shows the $k_{\text{eff}}$ values from Serpent and Moltres at
973 K and the corresponding salt density, while Table \ref{table:keff} shows
the $k_{\text{eff}}$ values for other temperatures at 100 K intervals. We
observe small discrepancies on the order of 100 pcm between the two codes
which we attribute to two main factors: the accuracy of the neutron diffusion
model, and the omission of the blanket tank structural material. The neutron
diffusion model is not as accurate as the other S$_{\text{N}}$ or
SP$_{\text{N}}$ deterministic methods nor the Monte Carlo approach in Serpent.
Regarding the omission of the blanket tank material, we replaced the
2 cm-thick structural material with blanket salt. This replacement may be
partly responsible for the higher $k_{\text{eff}}$ value calculated by Moltres
as the macroscopic fission cross sections of the blanket salt are non-zero for
the higher neutron energy groups. Nevertheless, the discrepancy is smaller
than the 228.5 pcm and 256.7 pcm discrepancies reported by Cervi et al.
\cite{cervi_development_2019} for their six-group $SP_3$ and neutron
diffusion methods, respectively, in OpenFOAM. The neutron diffusion model in
OpenFOAM is the same approach Aufiero et al. \cite{aufiero_development_2014}
used for their transient analysis of the \gls{MSFR}, albeit with one neutron
energy group.

\begin{table}[htb!]
    \small
	\centering
	\caption{$k_{\text{eff}}$ values from Serpent and Moltres at 973 K.}
	\begin{tabular}{l S c}
		\toprule
		{Code} & {$k_{\text{eff}}$} & {Difference wrt Serpent [pcm]}\\
		\midrule
		{Serpent} & 1.00662 \pm 0.00005 & {-}\\
		{Moltres with \glspl{DNP}} & 1.0079488 \pm 0.0000010 & 133\\
		{Moltres without \glspl{DNP}} & 1.0049369 \pm 0.0000010 & {-}\\
		\bottomrule
	\end{tabular}
	\label{table:keff}
\end{table}
%
\begin{table}[htb!]
    \small
	\centering
	\caption{$k_{\text{eff}}$ values from Serpent and Moltres at various
	temperatures from 800 K to 1400 K.}
	\begin{tabular}{S S S S}
		\toprule
		{Temperature [K]} & {$k_{\text{eff}}$ $\pm$ 1-$\sigma$ uncertainty
		(Serpent)} & {$k_{\text{eff}}$ (Moltres)} & {Difference wrt Serpent
		[pcm]}
		\\
		\midrule
		800  & 1.01996 \pm 0.00005 & 1.02117 & 121 \\
		900  & 1.01172 \pm 0.00005 & 1.01322 & 150 \\
		1000 & 1.00428 \pm 0.00005 & 1.00544 & 116 \\
		1100 & 0.99735 \pm 0.00005 & 0.99859 & 124 \\
		1200 & 0.99006 \pm 0.00005 & 0.99119 & 113 \\
		1300 & 0.98356 \pm 0.00005 & 0.98439 &  83 \\
		1400 & 0.97702 \pm 0.00005 & 0.97820 & 118 \\
		\bottomrule
	\end{tabular}
	\label{table:ktemp}
\end{table}

The absolute value of $k_{\text{eff}}$ largely impacts the steady-state
temperature of the reactor. We may adjust $k_{\text{eff}}$ by controlling
fissile inventory to raise or lower the operating temperatures and meet the
design specifications for inlet and outlet temperatures. For transient
analysis, the $\beta_{\text{eff}}$ and reactivity coefficients are arguably
more important as they dictate the duration and magnitude of the reactor
response to a transient initiator. The $\beta_{\text{eff}}$ values at 973 K,
shown in Table \ref{table:betaeff}, are in excellent agreement with a 2.89
pcm discrepancy.

\begin{table}[htb!]
	\centering
	\caption{$\beta_{\text{eff}}$ values from Serpent and Moltres at 973 K.}
	\begin{tabular}{l S S}
		\toprule
		{Code} & {$\beta_{\text{eff}}$ [pcm]} & {Difference wrt Serpent [pcm]}
		\\
		\midrule
		{Serpent} & 304.08 \pm .81 & {-}\\
		{Moltres} & 301.19 \pm .20 & 2.89\\
		\bottomrule
	\end{tabular}
	\label{table:betaeff}
\end{table}
%
\begin{figure}[htb!]
    \centering
    \includegraphics[width=.8\textwidth]{reactivity}
    \caption{Reactivity values from Serpent and Moltres. The Doppler
    reactivity values were calculated at a fixed density of 4.1249 g
    cm$^{-3}$. The density reactivity values were calculated at a fixed
    temperature of 973 K.}
    \label{fig:reactivity}
\end{figure}
%
\begin{table}[htb!]
	\centering
	\caption{Doppler, density, and total temperature coefficients
	for the temperature range of 800 K to 1400 K.}
	\begin{tabular}{l S S S S}
		\toprule
		{Code} & {$\alpha_D$ (log) [pcm]} & {$\alpha_D$ (linear) [pcm
		K$^{-1}$]} & {$\alpha_\rho$ [pcm K$^{-1}$]} & {$\alpha_T$ [pcm
		K$^{-1}$]} \\
		\midrule
		{Serpent} & -4034 \pm 14 & 3.737 \pm 0.013 & 3.424 \pm 0.013 & 7.165
		\pm 0.013 \\
		{Moltres} & {-} & {-} & {-} & 7.184\\
		\bottomrule
	\end{tabular}
	\label{table:alpha}
\end{table}

The temperature reactivity feedback arises mainly from Doppler broadening of
resonance absorption peaks and temperature-induced density changes. Although
Doppler coefficients typically show logarithmic dependence to temperature, we
report them, along with the other coefficients, as linear gradient
values of the reactivity given the relatively linear trend within the relevant
temperature range (Figure \ref{fig:reactivity}). Table \ref{table:alpha} shows
the temperature coefficients as described prior. The total temperature
coefficients from Serpent and Moltres show excellent agreement with a
discrepancy of 0.019 pcm K$^{-1}$.

Moltres also reproduced the six-group neutron spectrum very well from the
Serpent group constants. Figure \ref{fig:ntspec} compares the energy spectra
from Serpent and Moltres in the central fuel salt region. The six-group
neutron spectra overlap exactly over each other. More generally, the plot
shows the distinctive fast spectrum observed in the \gls{MSFR} with dips in
the spectrum corresponding to elastic scattering resonances from lithium and
fluorine. From this plot, we observe that the discrepancies in
$k_{\text{eff}}$ arise mainly from discretizing neutron energy into groups
rather than the neutron diffusion model itself. We could obtain a more
accurate representation of the neutronics in the \gls{MSFR} by using more
neutron energy groups but this would adversely impact simulation times in the
subsequent multiphysics finite element analyses.

\begin{figure}[htb!]
    \centering
    \includegraphics[width=.8\textwidth]{nt-spec}
    \caption{Reactivity values from Serpent and Moltres. The Doppler
    reactivity values were calculated at a fixed density of 4.1249 g
    cm$^{-3}$. The density reactivity values were calculated at a fixed
    temperature of 973 K.}
    \label{fig:ntspec}
\end{figure}

In summary, Moltres can replicate most of the relevant neutronics parameters
accurately with the group constant data from Serpent. While the
$k_{\text{eff}}$ values have discrepancies on the order of 100 pcm, they are
relatively small compared to results from other codes. Furthermore, the
$\beta_{\text{eff}}$ and temperature coefficients, which are important
parameters for modeling transient reactor behavior, are in excellent
agreement.

\section{Steady-State Results}

With the verification of Moltres' neutronics modeling capabilities in the
context of the \gls{MSFR}, we now move on to the multiphysics simulation
results. This section covers the steady-state multiphysics results from
Moltres.

The procedure for obtaining the steady-state results involved several steps
due to the highly coupled \glspl{PDE}. First, we ran a preliminary transient
simulation of fluid flow in the gls\MSFR} core, starting from zero inlet
velocity and gradually ramping it up to match the nominal flow rate (4.5 m$^3$
s$^{-1}$); otherwise Moltres had difficulty converging to the desired fully
developed flow profile. We imposed a parabolic flow profile at the inlet.
Next, we imported these fully developed flow values as initial values for
velocity in the actual transient simulation modeling the full coupled
neutronics and thermal-hydraulics. The initial values for the temperature and
neutron group flux distributions are 953 K and $1 \times 10^{14}$ cm$^{-2}$
s$^{-1}$ uniformly throughout the geometry. Finally, we assume that steady
state is reached when the volume integral values of every variable remain
constant (up to 6 sig. fig.) for at least four seconds in the simulation; this
time period corresponds to the nominal circulation time of the \gls{MSFR}.

For a direct comparison with the steady-state results from the Polimi/TUDelft
models, the bulk of our steady-state results do not have decay heat modeling.
Instead, we separately discuss the minor differences borne from decay heat
modeling in the last subsection.

Figure \ref{fig:flow-temp} shows the temperature and velocity fields
of the fuel salt in the core at steady state from Moltres and the
Polimi/TUDelft models. The results from Moltres show good qualitative
agreement with the Polimi/TUDelft models; we observe similar flow and hotspot
features in all three models. There is a large recirculation region near the
blanket tank walls arising from turbulent flow. Inertial forces dominate over
viscous forces to form this large eddy. The figure also shows two relatively
stagnant regions along the central axis at the top and bottom of the core.
Temperature hotspots form in these regions of recirculation as convection is
the dominant heat transfer mechanism. The maximum temperature from Moltres,
1279 K near the bottom of the recirculation zone, is closer to the maximum
temperature in the Polimi model ($\approx$ 1300 K) than the TUDelft model
($\approx$ 1200K). The minimum temperature is 922 K at the inlet. Figure
\ref{fig:flow} provides an alternate view of the flow profile through flow
streamlines superimposed on the velocity magnitude distribution. The fastest
salt flow occurs at the inlet, outlet, and at core half-height approximately
0.40 m away from the central axis.

\begin{figure}[htb!]
    \centering
    \begin{subfigure}[t]{.37\textwidth}
        \centering
        \includegraphics[width=\textwidth]{flow-temp}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{.625\textwidth}
        \centering
        \includegraphics[width=\textwidth]{flow-temp-fiorina}
    \end{subfigure}
    \caption{Temperature and velocity fields in the core from Moltres
    (left), Polimi (center), and TUDelft (right) models.}
    \label{fig:flow-temp}
\end{figure}

\begin{figure}[htb!]
    \centering
    \includegraphics[width=.6\textwidth]{flow}
    \caption{Fuel salt flow streamlines and velocity magnitude in the core.}
    \label{fig:flow}
\end{figure}

While the temperatures at the hotspots are well below the melting point of the
Ni-alloy structure (1500 K), they may cause undue thermal stress on the
blanket tank structure and induce relatively faster salt corrosion rates. A
sudden, large reactivity insertion could push fuel salt temperatures above the
melting point of the Ni-alloy and cause irreversible damage. Furthermore,
the reservoir of hot fuel salt may cause unpredictable behavior during
transient scenarios when the flow profile undergoes a drastic change.
Thus, Rouch et al. \cite{rouch_preliminary_2014} developed an improved
hourglass-shaped design to optimize flow distribution and prevent these
recirculation zones and hotspots from forming. A study of this new design
using Moltres is a potential subject for future work when a proper turbulence
model is in place.

@@

\subsection{Decay Heat}

A decay heat model effectively redistributes a fraction of the heat source
from the center of the core to the entire loop. Thus, we expect to observe
a slight flattening of the temperature distribution across the entire primary
loop.

\section{Transient Results}

As noted by Fiorina et al. \cite{fiorina_modelling_2014}, explicit decay heat
modeling has a negligible effect on reactivity-, pump-, and enchanced
cooling-driven transients. The Polimi model presented results with the decay
heat model for the loss of heat sink transient scenario only. For a fair
comparison, we also
